---
title: "Homework 5"
output: github_document
---

```{r, echo = FALSE, message=FALSE}
library(tidyverse)
library(p8105.datasets)
```

## Problem 1

Tidy the dataset

```{r}
homicide_df = read.csv("./data/homicide-data.csv", na = c("","Unknown")) %>% 
  mutate(city_state = str_c(city,state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved")
         
         ) %>%
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")

count(homicide_df, disposition)

```

Focus on Baltimore

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n)
    )

baltimore_test %>% 
  broom::tidy()
```

Create prop_test function

```{r}
prop_test_fuction = function(city_df){

  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
      )
  
  return(city_test)
  
}

```

Iterate across city

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_fuction),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

#nested_df %>% filter(city_state == "BaltimoreMD") %>% pull(test_results)


```


Plot showing estimates and confidence interval

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust =1))
  
```

Another way to do

```{r, eval = FALSE}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
    ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop_test),
    tidy_results = map(test_results, broom::tidy)
  )%>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```


## Problem 2

List of file names
```{r}
file_names = list.files("data/") 
file_names = paste0("data/",file_names)
```


Iterate over file names

```{r}
output = map(file_names, read_csv) 
```

Bind all files

```{r}
df = bind_rows(c(output[1:20]))
```

Add variable of arm category and subject id
```{r}
df = 
  df %>% 
  mutate(
    arm = c(rep("control",10),rep("experimental",10)),
    subject_id = c((1:10),(1:10))
  ) %>% 
  relocate(arm, subject_id)
```

Pivot the week variable

```{r}
df_tidy =
  df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_", # remove the prefix
    values_to = "value"
  ) %>% 
  view()
```


Make spaghetti plot
```{r}
ggplot(data = df_tidy, aes(x = week, y = value, group = subject_id)) +
  geom_line() +
  facet_grid(. ~ arm) +
  stat_smooth(aes(group = 1), method = "lm", se = FALSE) 
```

For subject in the control group, the trend of observation values did not change much over time, while in the experimental group, the observation values increased over time.

## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) 
```

Missing imputation:

For numeric variables, fill in missing values with the mean of non-missing values;
For character variables, fill in missing values with "virginica".

```{r}
missing_impute = function (v) {
  
  if (class(v) == "numeric"){
    v[is.na(v)] = mean(v,na.rm=TRUE)
  }
  if (class(v) == "character"){
    v[is.na(v)] = "virginica"
  }
  
  return (v)
}
```

Apply the missing imputation function to the columns of `iris_with_missing`

```{r}
iris = map(iris_with_missing[1:5], missing_impute) %>% 
  bind_rows(c(iris[1:5])) 
```


