---
title: "Homework 5"
output: github_document
---

```{r, echo = FALSE, message=FALSE}
library(tidyverse)
library(purrr)
```

## Problem 2

List of file names
```{r}
file_names = list.files("data/") 
file_names = paste0("data/",file_names)
```


Iterate over file names

```{r}
output = map(file_names, read_csv) 
```

Bind all files

```{r}
df = bind_rows(c(output[1:20]))
```

Add variable of arm category and subject id
```{r}
df = 
  df %>% 
  mutate(
    arm = c(rep("control",10),rep("experimental",10)),
    subject_id = c((1:10),(1:10))
  ) %>% 
  relocate(arm, subject_id)
```

Pivot the week variable

```{r}
df_tidy =
  df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_", # remove the prefix
    values_to = "value"
  ) %>% 
  view()
```


Make spaghetti plot
```{r}
ggplot(data = df_tidy, aes(x = week, y = value, group = subject_id)) +
  geom_line() +
  facet_grid(. ~ arm) +
  stat_smooth(aes(group = 1), method = "lm", se = FALSE) 
```

For subject in the control group, the trend of observation values did not change much over time, while in the experimental group, the observation values increased over time.

## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) 
```

Missing imputation:

For numeric variables, fill in missing values with the mean of non-missing values;
For character variables, fill in missing values with "virginica".

```{r}
missing_impute = function (v) {
  
  if (class(v) == "numeric"){
    v[is.na(v)] = mean(v,na.rm=TRUE)
  }
  if (class(v) == "character"){
    v[is.na(v)] = "virginica"
  }
  
  return (v)
}
```

Apply the missing imputation function to the columns of `iris_with_missing`

```{r}
iris = map(iris_with_missing[1:5], missing_impute) %>% 
  bind_rows(c(iris[1:5])) 
```


